---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```



[![Build Status](https://travis-ci.org/kota7/outreg.svg?branch=master)](https://travis-ci.org/kota7/outreg)

```{r, include=FALSE}
library(outreg)
```



# outreg
Create Regression Tables for Publication 

```{r, echo=FALSE}
fitlist <- list(lm(mpg ~ cyl, data = mtcars),
                lm(mpg ~ cyl + wt + hp, data = mtcars),
                lm(mpg ~ cyl + wt + hp + drat, data = mtcars))
knitr::kable(outreg(fitlist))
```

## Overview

`outreg` summarizes regression outcomes into a coefficient table in `data.frame` format.  Currently, `outreg` supports the following model fit objects:

- `lm`  : linear regression
- `glm` : logistic regression, poisson regression, etc
- `survreg` : survival regression, tobit regression, etc
- `ivreg` : instrument variable regression


## Usage

`outreg` takes a list of model fit objects as the main input, and returns a 
`data.frame` object where a model is represented in a column.

```{r}
library(outreg)
fitlist <- list(lm(mpg ~ cyl, data = mtcars),
                lm(mpg ~ cyl + wt + hp, data = mtcars),
                lm(mpg ~ cyl + wt + hp + drat, data = mtcars))
outreg(fitlist)
```


## Installation

This package is not on CRAN (yet).  
Please install it from the github repository.

```{r, eval=FALSE}
devtools::install_github('kota7/outreg')
```


## Examples


### Basic usage.
```{r}
library(outreg)
fitlist <- list(lm(mpg ~ cyl, data = mtcars),
                lm(mpg ~ cyl + wt + hp, data = mtcars),
                lm(mpg ~ cyl + wt + hp + drat, data = mtcars))
outreg(fitlist)
```

### If regression list is named, the names are used as column names.
```{r}
outreg(setNames(fitlist, c('small', 'medium', 'large')))
```

### May choose statistics to display and which stats to put "stars" on.
```{r}
outreg(fitlist, pv = TRUE, se = FALSE, starred = 'pv')
```





### Poisson regression.
```{r}
counts <- c(18,17,15,20,10,20,25,13,12)
outcome <- gl(3,1,9)
treatment <- gl(3,3)
fitlist2 <- list(glm(counts ~ outcome, family = poisson()),
                 glm(counts ~ outcome + treatment, family = poisson()))
outreg(fitlist2)
```



### Logistic regression.
```{r}
fitlist3 <- list(glm(cbind(ncases, ncontrols) ~ agegp,
                     data = esoph, family = binomial()),
                 glm(cbind(ncases, ncontrols) ~ agegp + tobgp + alcgp,
                     data = esoph, family = binomial()),
                 glm(cbind(ncases, ncontrols) ~ agegp + tobgp * alcgp,
                     data = esoph, family = binomial()))
outreg(fitlist3)
```


### Survival regression
```{r}
library(survival)
fitlist4 <- list(survreg(Surv(time, status) ~ ph.ecog + age,
                         data = lung),
                 survreg(Surv(time, status) ~ ph.ecog + age + strata(sex),
                         data = lung))
outreg(fitlist4)
```



### Tobit regression
```{r}
fitlist5 <- list(survreg(Surv(durable, durable>0, type='left') ~ 1,
                 data=tobin, dist='gaussian'),
                 survreg(Surv(durable, durable>0, type='left') ~ age + quant,
                 data=tobin, dist='gaussian'))
outreg(fitlist5)
```


### Combine instrument variable regression and linear regression.
```{r, message=FALSE}
library(AER)
data("CigarettesSW", package = "AER")
CigarettesSW$rprice <- with(CigarettesSW, price/cpi)
CigarettesSW$rincome <- with(CigarettesSW, income/population/cpi)
CigarettesSW$tdiff <- with(CigarettesSW, (taxs - tax)/cpi)

fitlist6 <- list(OLS = lm(log(packs) ~ log(rprice) + log(rincome),
                          data = CigarettesSW, subset = year == "1995"),
                 IV1 = ivreg(log(packs) ~ log(rprice) + log(rincome) |
                             log(rincome) + tdiff + I(tax/cpi),
                             data = CigarettesSW, subset = year == "1995"),
                 IV2 = ivreg(log(packs) ~ log(rprice) + log(rincome) |
                             log(population) + tdiff + I(tax/cpi),
                             data = CigarettesSW, subset = year == "1995"))
outreg(fitlist6)
```
